Social Computing Article\thanks{This title is temporary}

### 2013-01-16 Article.tex
corrigi algumas coisas e adicionei o abstract

\begin{abstract}
  Abstract
\end{abstract}

@@

In order to validate the algorithm as a social problem solving technique, we have modelled the collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through it and tested it over a set of {\em Sudoku} instances.

@@

We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent in order to compose a simulated graphic interface. As a result, each agent visualizes some neighbours before or after others. Secondly, we translated the above mathematical model into an message-selecting metric in which the solution selected by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.

@@

In our modelling, we associate each agent with a numerical parameter determining the probability of this agent to guess when incapable of applying a typical {\em Sudoku} solving strategy.

@@

Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob}). The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions. Also, as shown in Figure~\ref{fig:copy_guess_free_prob_num_solution_reached}, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.

@@

Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. Another chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly.

As can be seen in Figures ~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.

@@

Even so, that behaviour was observed in human networks. \cite{farenzena:collabem} has suggested that human beings behave like that because in the real world the environment continuously selects against ineffective solutions, since a bad choice in solving a real world problem might cause and agent to cease communication. Since neither the original experiments nor our simulation included such a mechanism, the advantages of that process have not been observed, but they might already be good enough that it may not justify the effort for the agents to evaluate the solutions.

@@

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for agent-based social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. With these results in mind, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.

>>>>

\begin{abstract}
Social collaboration has been shown to facilitate problem-solving activity in a diverse set of environments. Nevertheless, if not well designed, a social human computation system may achieve results as poor as those of a single human subject performing a task. This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks. We present a novel method for agent-based social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks. Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people. Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks. We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
\end{abstract}

@@

In order to validate the algorithm as a social problem solving technique as well as establishing a comparison between agent-based simulations and tests with human subjects, we have modelled the collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of {\em Sudoku} instances.

@@

We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent in order to compose a simulated graphic interface. As a result, each agent visualizes some neighbours before or after others. Secondly, we translated the above mathematical model into a message-selecting metric in which the solution selected by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.

@@

In our modelling, we associate each agent with a numerical parameter determining the probability this agent has to guess when incapable of applying a typical {\em Sudoku} solving strategy.

@@

Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. This was our hypothesis, and our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob}). The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions. Also, as shown in Figure~\ref{fig:copy_guess_free_prob_num_solution_reached}, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.

@@

Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly. Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks are able to respond positively to the employment of evaluation functions.

As can be seen in Figure ~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.

@@

Even so, that behaviour was observed in human networks. Farenzena~\cite{farenzena:collabem} has suggested that human beings behave like that because in the real world the environment continuously selects against ineffective solutions, since a bad choice in solving a real world problem might cause and agent to cease communication. Since neither the original experiments nor our simulation included such a mechanism, the advantages of that process have not been observed, but they might already be good enough that it may not justify the effort for the agents to evaluate the solutions.

@@

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for agent-based social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. Thus, having in mind the fact that the strategies employed by human subjects are often not the most efficient, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.
